SunPy - Python for Solar Physics

### 2014-01-30 2-Data_Types.tex
Changes mainly to the visualisation section

SunPy provides data strucutures that are specifically designed for the
three primary varieties of solar physics data: images, time series, and
spectra. These core data types are supported by SunPy's classes:
\texttt{Map} (2D spatial data), \texttt{LightCurve} (1D temporal series)
and \texttt{Spectrum} and \texttt{Spectrogram} (1D and 2D spectra).

These classes allow access to the data
and associated metadata and provide appropriate convenience functions to
enable analysis and visualisation. For each of these classes, the data is
stored in the \texttt{data} attribute while the metadata should be stored 
in the \texttt{meta} attribute. (Curently, only \texttt{Map} has this feature fully implemented) 
% schriste - can't we just quickly fix this? should be easy enough.
% dps - Spectrogram does not contain meta either! I would suggest
%(Curently, this is just supported by Map, but the other data types will 
%include such attribute soon.)
%SJM: oh what, drop it all together.
It is possible to instantiate the
data types from various
different sources: e.g., files, URLs, arrays.  
In order to provide instrument-specific specialisation, the core SunPy classes 
make use of subclassing; e.g., \texttt{Map} has an \texttt{AIAMap} 
sub-type for data from the \textit{SDO}/AIA instrument.

@@

This design philosophy makes the behaviour of SunPy's visualisation 
routines intuitive to those who already understand the \texttt{matplotlib}
interface, as well as allowing the use of the standard 
\texttt{matplotlib} commands to manipulate the plot parameters (e.g. title, axes).
Data visualisation is provided by two functions: \texttt{peek()}, for quick 
plotting, and \texttt{plot()}, for plotting with more fine-grained control that 
integrates with \texttt{matplotlib}.

>>>>

SunPy currently provides data strucutures that are specifically designed for the
three primary varieties of solar physics data: images, time series, and
spectra. These core data types are supported by SunPy's classes:
\texttt{Map} (2D spatial data), \texttt{LightCurve} (1D temporal series)
and \texttt{Spectrum} and \texttt{Spectrogram} (1D and 2D spectra).

These classes allow access to the data
and associated metadata and provide appropriate convenience functions to
enable analysis and visualisation. For each of these classes, the data is
stored in the \texttt{data} attribute while the metadata should be stored 
in the \texttt{meta} attribute. (Curently, only \texttt{Map} has this feature 
fully implemented.) 
% schriste - can't we just quickly fix this? should be easy enough.
% dps - Spectrogram does not contain meta either! I would suggest
%(Curently, this is just supported by Map, but the other data types will 
%include such attribute soon.)
%SJM: oh what, drop it all together.
%SJM see PR #785 to the main repo.
It is possible to instantiate the
data types from various
different sources: e.g., files, URLs, arrays.  
In order to provide instrument-specific specialisation, the core SunPy classes 
make use of subclassing; e.g., \texttt{Map} has an \texttt{AIAMap} 
sub-type for data from the \textit{SDO}/AIA instrument.

@@

This design philosophy makes the behaviour of SunPy's visualisation 
routines intuitive to those who already understand the \texttt{matplotlib}
interface, as well as allowing the use of the standard 
\texttt{matplotlib} commands to manipulate the plot parameters (e.g. title, axes).
Data visualisation is provided by two functions: \texttt{peek()}, for quick 
plotting, and \texttt{plot()}, for plotting with more fine-grained control.
